Inferring cosmology from gravitational waves using non-parametric detector-frame mass distribution

### 2024-08-05 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}[h]
    \script{plot_simulation_transformation.py}
    \includegraphics[width=\linewidth]{figures/simulation_transformation.pdf}
    \caption{
        The upper panel shows the source-frame $m_1$ population distribution, which we chose as the true population model.
        The lower panel shows the transformed detector-frame $m^z_1$ population distributions for different $H_0$.
        The source-frame population distribution is redshifted towards higher masses as $H_0$ increases, as $m^z_1 = m_1(1+z)$ and $z$ increases with $H_0$ for a given $d_L$.
        The low-mass peak is suppressed due to the selection function.
    }
    \label{fig:simulation_transformation}
\end{figure}

@@

\begin{figure}[h]
    \script{plot_simulation_comparison.py}
    \includegraphics[width=\linewidth]{figures/simulation_comparison.pdf}
    \caption{
        \todo{Add caption}
    }
    \label{fig:simulation_comparison}
\end{figure}

% $H_0$ only
\begin{figure}[h]
    \script{plot_simulation_result_H0.py}
    \includegraphics[width=\linewidth]{figures/simulation_result_H0.pdf}
    \caption{
        \todo{Add caption}
    }
    \label{fig:simulation_result_H0}
\end{figure}

>>>>

\begin{figure}[h]
    \script{plot_simulation_transformation.py}
    \includegraphics[width=\linewidth]{figures/simulation_transformation.pdf}
    \caption{
        The upper panel shows the source-frame $m_1$ population distribution, which we chose as the true population model.
        The lower panel shows the transformed detector-frame $m^z_1$ population distributions for different $H_0$, where the corresponding $H_0$ is shown in the legend.
        The source-frame population distribution is redshifted towards higher masses as $H_0$ increases, as $m^z_1 = m_1(1+z)$ and $z$ increases with $H_0$ for a given $d_L$.
        The low-mass peak is suppressed due to the selection function.
    }
    \label{fig:simulation_transformation}
\end{figure}

@@

\begin{figure}[h]
    \script{plot_simulation_comparison.py}
    \includegraphics[width=\linewidth]{figures/simulation_comparison.pdf}
    \caption{
        The blue line and bands are the ones from Fig.~\ref{fig:simulation_reconstruction}, which represent the reconstructed observed population.
        The other colored lines are the ones from Fig.~\ref{fig:simulation_transformation}, which represent the transformed population for different $H_0$.
        The shaded regions represent the boundaries for the calculation of $d_\mathrm{JS}$, i.e., the $d_\mathrm{JS}$ calculation only considers the non-shaded region.
    }
    \label{fig:simulation_comparison}
\end{figure}

% $H_0$ only
\begin{figure}[h]
    \script{plot_simulation_result_H0.py}
    \includegraphics[width=\linewidth]{figures/simulation_result_H0.pdf}
    \caption{
        The histogram shows the distribution of the optimized $H_0$.
        The vertical blue line and shaded regions represent the median, 68\%, and 90\% credible intervals of the distribution.
        The vertical orange line represents the true $H_0$ we used to generate the mock data.
        Note that the distribution only shows the uncertainty in the reconstruction.
        The uncertainty in the comparison is not considered in the distribution.
    }
    \label{fig:simulation_result_H0}
\end{figure}
